---
title: "Milestone 5"
author: "Liz Masten"
date: "3/29/2020"
output: bookdown::pdf_document2
bibliography: bib2.bib
biblio-style: apalike 
link_citations: TRUE
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

knitr::write_bib(c("knitr", "stringr"), "bib2.bib", width = 60)

library(foreign)
library(tinytex)
library(gt)
library(bookdown)
library(stargazer)
library(bibtex)
library(yaml)
library(knitcitations)
library(tidyverse)
```

```{r}

#Here is the cleaned data, available in GitHub repo. 

data <- read.dta("fpy_replication_data_jop_2012.dta")

# 1) A footnote with your repo url and some verbiage about “All analysis for this paper is available . . .”

# 4) A 300 – 500 word overview of your replication paper. What analysis did they run? What did they conclude?

```
I am planning to replicate a paper by Michael Findley, James Piazza, and Joseph Young titled "Games Rivals Play: Terrorism in International Rivalries," appearing in The Journal of Politics, Vol. 74, No. 1, January 2012, Pp. 235-248. This paper analyzes transnational terrorism as a component of interstate rivalries, specifically focusing on the use of terrorism in proxy warfighting. 

Games Rival’s Play: Terrorism in International Rivalries Michael Findley, James Piazza, and Joseph Young argue in their paper Games Rivals Play: Terrorism in International Rivalries that interstate rivalries are a positive predictor of transnational terrorist activity. In other words, terrorist attacks are more likely to occur in the context of a rivalry between two states than in the absence of such a rivalry. They empirically test their hypothesis by analyzing “politically relevant directed state dyads,” meaning that they focus on country-level factors in states that sponsor terrorism as well as target states, while ignoring the states that are unlikely to interact at all in the international system. This use of politically relevant dyads allows the authors to incorporate covariates (rivalry, joint democracy, contiguity, and capability ratio) as controls, as well as practice good statistical practices by discounting irrelevant dyads that would increase the number of observations, thus increasing the likelihood of spurious statistical significance.^[All analysis for this paper is available in my GitHub: https://github.com/LizMas/ms_5]

My thanks go to Professor Erica Chennoweth for suggesting this paper.


```{r}

#table using gt package 

table <- data %>% 
  #filter to after 1990 because the table was too big otherwise and I'd never actually do a table like that anyway 
  filter(year >= 1990) %>% 
  select(year, terrorCounts) %>% 
  group_by(year) %>% 
  summarise(events = sum(terrorCounts))


gt_table <- gt(table) %>% 
            tab_header(title = "Terror Attacks per Year")

gt_table

```


```{r}

#prep a quick regression for stargazer table example 

x <- data %>% 
  select(year, terrorCounts, rivalry) %>% 
  group_by(year) %>% 
  drop_na()

model_x <- glm(rivalry ~ terrorCounts, data = x)

```

```{r, results='asis'}

#To get stargazer to work with a pdf output, I had to put results = 'asis' in the code chunk. 

#Using the normal output method I used in the past gave me a gross looking table, so I changed it to header = FALSE and type = 'latex' to make it compatable with the pdf output, I suppose. 

stargazer(model_x, header=FALSE, type='latex')

```


# References {-}

```{r generated bibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "bib2.bib")
read.bibtex(file = "article.bib")

#This is still a mess, but I can't for the life of me get the # off. Also, there has to be a better way to 1) not get the bib.bib/ bib2.bib file to overwrite with the default nonsense that R does and 2) combine the .bib files so I don't have to call individual files like article.bib. This was my work around for now... 
 
```
# Appendix {-}

